---
title: "Importing Data"
author: "Amanda Mae Woodward"
date: "2023-02-20"
output: html_document
---

## Learning Outcomes for This video:

By the end of the video, you should be able to:
- Describe File Structures and Working Directories
- Import Data to R Studio
- Recognize Common Errors with importing data

### Learning Outcome #1:  Describe File Structures and Working Directories

#### File Structure:

#### Working Directory: 
```{r}
getwd()
#setwd(dir = )
```

### Learning Outcome #2: Import Data to R Studio

#### From an R Project
```{r}
library(readr)
parksAndRecData <- read_csv("parksAndRecData.csv")
```

#### Using Import Dataset
```{r}
PaRdata <- read.csv("~/Desktop/R Studio Videos/parksAndRecData.csv")
#change file path to wherever it's saved on your computer 
```

#### Using Code 
```{r}
dat<- read.csv("~/Desktop/R Studio Videos/parksAndRecData.csv")

```

### Learning Outcome #3: Common Errors with importing data

#### Incorrect File path
```{r}
ParksData<- read.csv("parksandRecData.csv")
```

#### Not including code in Markdown File 
```{r}
ParksData
```

